### 2019-10-03 thesis/txt/1-related-work.tex
filling various sections with points on what to write about

\chapter{Related Work}
\todo{introduction \& glue text}

\section{CI Research}
\mention{look into proksch papers}
Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development. Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google. In addition most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones. They determined that testing failures outweigh compilation errors. Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.

@@

IR papers, maybe something about keyword search?

>>>>

\chapter{Related Work}
\todo{introduction \& glue text}
This section presents various research works adjecent or foundational for our work. Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation. We differentiate our work from the more common production runtime log analysis and cover different information extraction and retrieval techniques. Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.

\section{Continuous Integration Research}
\mention{look into proksch papers}
Various researchers have analyzed industrial and open source logs for failure reasons and their impact on development. Seo et al.~\cite{seo2014programmers} found that few error types such as dependency mismatches are the most prominent cause of build failures at Google. In addition most failures are resolved within two builds. Vassallo et al.~\cite{vassallo2017a-tale} compared open source projects in Java to industrial ones. They determined that testing failures outweigh compilation errors. Open source builds fail most often because of unit tests, whereas release preparations is the primary cause in industrial projects. Beller et al.~\cite{beller2017oops} showed that testing is central to continuous integration when evaluating Travis CI logs for Java and ruby builds. They observed very different kinds, failure rates and numbers of test between programming languages and explained that the low failure rates hint at code being tested before it is sent to the CI server.

@@

\mention{IR papers, maybe something about keyword search?}

### 2019-10-03 thesis/txt/2-models.tex
filling various sections with points on what to write about

\chapter{Information Extraction Techniques}
\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
overview introduction text
\label{models}

\section{Our Model for IE Techniques}
\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
\section{Our Model for extraction tasks}
\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
\section{Our Model for extractable information}
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

\section{PROSE Program Synthesis}
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}

\section{IR Similarity}
\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}

\section{Keyword search}
\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}

\section{further techniques}

>>>>

\chapter{Information Extraction Techniques}
\label{models}
\includegraphics[page=1, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
Many different information extraction techniques ... this section describes the concepitonal / theoretical results of our thesis ... 
We create a model to characterize BLIE techniques so we can discuss their similarities and differences more clearly. 
Additionally we present a complimentary model for IE tasks, to describe use cases for BLIE techniques in a structured way.
From our analysis of build logs we share our notion of the extractable information within a build log.

\section{Our Model for IE Techniques}
\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
A build log information extraction technique (BLIE technique) consumes a build log (text file) and produces a certain output (text). \todo{make picture, output can be contained in log or not, can be continuous substring or selected lines etc.}.
\begin{itemize}
  \item{Target}{Extractable Information} each extraction technique \todo{instantiation!} targets a specific information
  \item{Setup Overhead}{Time}
  \item{Performance}{Performance} split into learning performance
\end{itemize}

Example instantiations of this task later in this chapter, namely for the three techniques we are comparing: PROSE program synthesis, IR text similarity, and simple keyword search. \todo{ref?}

\section{Our Model for extraction tasks}
\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
aims to describe an information extraction task of a developer or a researcher.
\begin{itemize}
  \item \todo{describe all classes}
  \item{Setup Overhead}{Time}
  \item{Performance}{Performance} split into learning performance
\end{itemize}
\todo{give 2-3 concrete example instantiations here}

\section{Our Model for extractable information}
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
during our inital exploration \& data collection for the Failing Build Log Data Set, wanted to get an impression about the information one would want to extract from a build log
\begin{itemize}
  \item \todo{describe all classes}
  \item{Setup Overhead}{Time}
  \item{Performance}{Performance} split into learning performance
\end{itemize}
\todo{differentiate Travis CI specific things, explain high variability for instantiations}
\todo{give at least one concrete example instantiation, best from a log in the data set, not too long so maybe it goes in the abstract?, picture/graphic with marked parts here?}

\section{PROSE Program Synthesis}
\includegraphics[page=2, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?, describe regex programs}

\section{IR Similarity}
\includegraphics[page=3, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}

\section{Keyword search}
\includegraphics[page=4, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/RetreatSeptemberSlides.pdf}
\todo{explanation of process, the way our tool does it, instantiate model of extraction technique, probably no additional theoretical stuff really needed here?}

\section{further techniques}
\todo{maybe: instantiate model, or at least partly talk about it}
\todo{diffing, manual regex?, other summarization?, BART? <- we could reference that from related work then}

### 2019-10-03 thesis/txt/3-data-set.tex
first complete draft thesis introduction, chapters and structure in separate files
put pictures for explanations in various sections
filling various sections with points on what to write about

\chapter{Information Extraction Techniques}
overview introduction text
\label{models}

\section{Our Model for IE Techniques}
\section{Our Model for extraction tasks}
\section{Our Model for extractable information}

\section{PROSE Program Synthesis}

\section{IR Similarity}

\section{Keyword search}

\section{further thechniques}

>>>>

\chapter{The Failing Build Logs Data Set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

\label{data-set}
\section{Motivation}
originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how strutured or unstructured they are.
Then labeling of one build log information, namely the reason the build failed, as well as keywords and stuructural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results

\section{Log Collector}
ghtorrent, travis, implementation description, reference CLI interface nicely?
describe special cases?
\todo{image! like in travistorrent paper}

\section{Collection Process}
differentiate original collection and for data set?
actual instantiation: 30 langs, 3 repos that use Travis, 10 failed logs each -> 80 useable, x logs
our impression?
\todo{image!}

\section{Labeling (better name?)}
  \subsection{Build Failure Reason}

    \paragraph{Description}
    WHY? one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability
    \paragraph{Labeling Process}

  \subsection{Keywords}

    \paragraph{Description}

    \paragraph{Labeling Process}

  \subsection{Categories}

    \paragraph{Description}

    \paragraph{Labeling Process}

\section{Validation of our data set}
\todo{copy over from md doc}

\subsection{Inter-Rater Reliability}

\subsection{Sending Mails out to developers}

### 2019-10-03 thesis/txt/4-tool.tex
first complete draft thesis introduction, chapters and structure in separate files
put pictures for explanations in various sections
filling various sections with points on what to write about

\chapter{Information Extraction Techniques}
overview introduction text
\label{models}

\section{Our Model for IE Techniques}
\section{Our Model for extraction tasks}
\section{Our Model for extractable information}

\section{PROSE Program Synthesis}

\section{IR Similarity}

\section{Keyword search}

\section{further thechniques}

>>>>

\chapter{Our Information Extraction Tool}
\label{implementation}
describe implemantation of Tool
\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

\section{common interface} 
unification tool, reference CLI somehow nicely?,
ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)

\section{PROSE Program Synthesis}
implementation details :)
C#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)

\section{IR Similarity}
impl details,
R, text2vec, tokenized vectors, impl of preprocessing?
don't repeat from IE models section!

\section{Keyword search}
impl details,
R, simple!

### 2019-10-03 thesis/txt/6-conclusion.tex
first complete draft thesis introduction, chapters and structure in separate files
filling various sections with points on what to write about

\chapter{Technique Comparison Study}
\label{evaluation}

\section{Study Design}

\section{Study Results}

\section{resulting Reccomending Scheme}

>>>>

\chapter{Conclusion}
\label{conclusion}
answer research questions (again)

\section{Future Work}
\begin{itemize}
  \item more techniques (which kinds of techniques? express in model! e.g. diffs might not work?), same evaluation, ir automated keyword search/expansion
  \item other works with data set: what else could this be used for?
  \item refine / improve techniques with the results automatically obtainable for evaluation with data set
    \begin{itemize}
      \item pbe: ranking adjustments, or even new dsl components?
      \item ir: meta-parameter optimizations
    \end{itemize}
  \item socio-technical: how do developers interact with buildlogs?
\end{itemize}
